Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-15 main.tex
last changes before submission (done on Friday)

\newcommand{\heft}{\algo{HEFT}\xspace}
\newcommand{\heftmm}{\algo{HEFTM\_MM}\xspace}
\newcommand{\heftbl}{\algo{HEFTM\_BL}\xspace}
\newcommand{\heftblc}{\algo{HEFTM\_BLC}\xspace}

@@

    For state-of-the-art memory prediction methods, a cold-start median prediction error for heterogeneous infrastructures of approximately 15\% is shown~\cite{TODO}.
    \AB{I have no idea what to cite there... Svetlana?}
    Online prediction methods were able to significantly reduce the error during runtime, with the reduction reaching up to one-third of the cold-start error~\cite{baderDiedrichDynamic2023,witt2019learning}.
%For instance, Nadeen~et~al.\cite{} report an error of 10\%, 11\%, and 15\% while the task prediction errors shows a normal and exponential distribution.
%Bader~et~al.~ report a prediction error between 13\% and 17\% for their method, showing an exponential task error distribution.
% @Svetlana, willst du sowas für deine Experimente? Also die Daten, welche du dann konfigurieren kannst?
    Such a dynamic execution environment requires a dynamic scheduling method where the schedule can be recomputed during the workflow execution.

@@

    All algorithms are implemented in C++ and compiled with g++ (v.8.5.0).
    The experiments are managed by simexpal~\cite{DBLP:journals/algorithms/AngrimanGLMNPT19} and executed on workstations with 192 GB RAM and 2x 12-Core Intel Xeon 6126 @3.2 GHz
    and CentOS 8 as OS.
    Code, input data, and experiment scripts are available to allow reproducibility of results, at~\skug{\url{insert link}}.

@@

Note that in both clusters, we set the size of the communication buffer to be equal
to the memory size. \todo[inline]{Is this correct? }

@@

\AB{Any info on success rate of adaptive heuristic compared to static ones? 
For which cluster do we have some results? }

>>>>

\newcommand{\heft}{\algo{HEFT}\xspace}
\newcommand{\heftmm}{\algo{HEFTM-MM}\xspace}
\newcommand{\heftbl}{\algo{HEFTM-BL}\xspace}
\newcommand{\heftblc}{\algo{HEFTM-BLC}\xspace}

@@

    For state-of-the-art memory prediction methods, a cold-start median prediction error for heterogeneous infrastructures
    of approximately 15\% is shown~\cite{malik2013execution}.
    Online prediction methods were able to significantly reduce the error during runtime, with the reduction reaching up to one-third of the cold-start error~\cite{baderDiedrichDynamic2023,witt2019learning}.
%For instance, Nadeen~et~al.\cite{} report an error of 10\%, 11\%, and 15\% while the task prediction errors shows a normal and exponential distribution.
%Bader~et~al.~ report a prediction error between 13\% and 17\% for their method, showing an exponential task error distribution.
% @Svetlana, willst du sowas für deine Experimente? Also die Daten, welche du dann konfigurieren kannst?
    Such a dynamic execution environment requires a dynamic scheduling method where the schedule can be recomputed during the workflow execution.

@@

    All algorithms are implemented in C++ and compiled with g++ (v.8.5.0).
    The experiments are managed by simexpal~\cite{DBLP:journals/algorithms/AngrimanGLMNPT19} and executed on workstations with 192 GB RAM and 2x 12-Core Intel Xeon 6126 @3.2 GHz
    and CentOS 8 as OS.
    Code, input data, and experiment scripts are available to allow reproducibility of results, at~\url{https://zenodo.org/records/13919214}~and~\url{https://zenodo.org/records/13919302}.

@@

Note that in both clusters, we set the size of the communication buffer to be equal
to ten times the the memory size.

@@
